\thetitle

### 2017-12-05 TeX/manuscript.tex
added some diagrams

 Figure \ref{fig:sig-neuron} illustrates a neuron that receives three ordered inputs.

 \begin{figure}[h]
 \centering
 \begin{tikzpicture}

@@

 \begin{figure}
 \centering
 \begin{tikzpicture}

@@

>>>>

 \begin{figure}[!htb]
 \centering
 \begin{tikzpicture}

@@

 \begin{figure}[!htb]
 \centering
 \begin{tikzpicture}

@@

	Syntax trees such as the ones shown above work perfectly, since each contain exclusively arithmetic or logical computations. In the trees shown below, however, the two computation classes are combined through multiplication and addition. The tree's results depend entirely on how we choose to evaluate $2 * True$ and $2 + True$.

 \begin{figure}[!htb]
 \centering
 \begin{tikzpicture}

	\node [bordered,red] (v1) at (0.5,8) {5};
	\node [bordered,red] (v5) at (2.5,8) {3};
	\node [bordered,red] (v4) at (5.5,8) {False};
	\node [bordered,red] (v3) at (7.5,8) {True};

	\node [bordered,blue] (v6) at (6.5,9) {OR};
	\node [bordered,blue] (v2) at (1.5,9) {-};

	\node [bordered,blue] (v7) at (4,9.5) {*};

	\node [black] (v9) at (4,12) {\Huge eval($2 * True$)};

	\draw [con] (v7) edge (v9);

	\node [bordered,red] (vv1) at (10.5,8) {5};
	\node [bordered,red] (vv5) at (12.5,8) {3};
	\node [bordered,red] (vv4) at (15.5,8) {False};
	\node [bordered,red] (vv3) at (17.5,8) {True};

	\node [bordered,blue] (vv6) at (16.5,9) {OR};
	\node [bordered,blue] (vv2) at (11.5,9) {-};

	\node [bordered,blue] (vv7) at (14,9.5) {+};

	\node [black] (vv9) at (14,12) {\Huge eval($2 + True$)};

	\draw [con] (vv1) edge (vv2);
	\draw [con] (vv3) edge (vv6);
	\draw [con] (vv4) edge (vv6);
	\draw [con] (vv5) edge (vv2);

	\draw [con] (vv2) edge (vv7);
	\draw [con] (vv6) edge (vv7);

	\draw [con] (vv7) edge (vv9);

 \end{tikzpicture}
 \caption{Abstract Syntax Trees of logical and arithmetic operations.} 
 \end{figure}
